Presentation Title

### 2017-03-16 presentation.tex
Interesting research question on ZK

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-good}
  \centering
  \caption{\emph{TX block} is a six-tuple: $t_{i,j} = (\texttt{h}(b_{i,j-1}),
    h_s, h_r, s_s, s_r, m)$, one transaction results in two TX blocks---\emph{a
      pair}.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-bad}
  \centering
  \caption{Fork is two correctly signed TX blocks that has the same $h_s$ but
    involve different receivers. Only one TX block may be in consensus.}
  \end{figure}

@@

\begin{frame}{TrustChain}
  \begin{itemize}
    \item Everyone has their own chain
    \item Transactions are on arbitrary data $m$
    \item Transactions make the chains intertwined
    \item Transactions are irrefutable due to hash pointers
    \item No consensus (my thesis)
  \end{itemize}
\end{frame}

@@

\subsection{Consensus}
\begin{frame}{Consensus}
  \begin{enumerate}
    \item Nodes send CP blocks to the promoters.
    \item The promoters' identities are encoded in the consensus result.
    \item Promoters run the some asynchronous BFT consensus algorithm to agree on
      a set of CP blocks---$\mathcal{C}_r$.
    \item $n = 3t + 1$ is the optimal for BFT consensus.
    \item $\mathcal{C}_r$ and the signatures are disseminated.
    \item Nodes create new CP blocks when they receive $t + 1$ good signatures and
      $\mathcal{C}_r$.
  \end{enumerate}

  \begin{theorem}
    Assuming the promoters satisfy $n = 3t + 1$. The promoter registration and
    the consensus protocol satisfied agreement, total order and liveness.
  \end{theorem}
\end{frame}

@@

  \begin{theorem}
    If at least one party of every transaction is honest, then forking and other
    forms of tampering is guaranteed to be detected if the malicious party is
    alive.
  \end{theorem}
\end{frame}

\subsection{Implementation}
\begin{frame}{Implementation}
  \begin{itemize}
    \item Currently on going---using Python and Twisted
    \item Completed BFT consensus algorithm
    \item Completed local TrustChain
    \item Next step is networked TrustChain and validation protocol
  \end{itemize}
\end{frame}
\end{document}

>>>>

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-good}
  \centering
  \caption{Every node has a chain. \emph{TX block} is a six-tuple: $t_{i,j} =
    (\texttt{h}(b_{i,j-1}), h_s, h_r, s_s, s_r, m)$, one transaction results in
    two TX blocks---\emph{a pair}.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-bad}
  \centering
  \caption{Fork is two correctly signed TX blocks that belong to the same sender
    and has the same hash pointer but involve different receivers. Only one TX
    block may be in consensus.}
  \end{figure}

@@

\begin{frame}{TrustChain}
  \begin{itemize}
    \item Everyone has their own chain
    \item Transactions are on arbitrary data $m$
    % \item Transactions make the chains intertwined
    \item Transactions are irrefutable due to hash pointers
    \item No consensus (my thesis)
  \end{itemize}
\end{frame}

@@

\subsection{Consensus}
\begin{frame}{Consensus}
  \begin{enumerate}
    \item Nodes send CP blocks to the promoters.
    \item The promoters' identities are encoded in the consensus result.
    \item Promoters run the some asynchronous BFT consensus algorithm to agree on
      a set of CP blocks---$\mathcal{C}_r$.
    \item $n \ge 3t + 1$ is the optimal for BFT consensus.
    \item $\mathcal{C}_r$ and the signatures are disseminated.
    \item Nodes create new CP blocks when they receive $t + 1$ good signatures and
      $\mathcal{C}_r$.
  \end{enumerate}

  \begin{theorem}
    Assuming the promoters satisfy $n \ge 3t + 1$. The promoter registration and
    the consensus protocol satisfies agreement, total order and liveness.
  \end{theorem}
\end{frame}

@@

  \begin{theorem}
    If at least one party of every transaction is honest, then forking and other
    forms of tampering is guaranteed to be detected if the malicious party is
    alive.
  \end{theorem}

  \begin{block}{Question}
    Given a starting digest and an ending digest, is it possible for the prover
    to proof to the verifier that it has a set of blocks linked by hash pointers
    that ``fits'' inside those digests in \emph{zero knowledge}.
  \end{block}
\end{frame}

\subsection{Implementation}
\begin{frame}{Implementation}
  \begin{itemize}
    \item Currently on going---using Python and Twisted
    \item Completed BFT consensus algorithm
    \item Completed local TrustChain with Checkpoints
    \item Next step is networked TrustChain and validation protocol
  \end{itemize}
\end{frame}
\end{document}
